\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-26 paper.tex
fix styling

% useful packages
\usepackage[utf8]{inputenc}
\usepackage{minted}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{graphicx} % for images
\usepackage[gen]{eurosym} % for literally just the euro symbol

\usepackage{lipsum}   % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
\usepackage[page, titletoc, title]{appendix}
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref}      % hyperlinks

% more breathing room
\linespread{1.5}
\setminted{fontsize=\small,baselinestretch=1}

@@

% stuff for LaTeX to know
\bibliography{references}
\graphicspath{ {./images/} } % put images in here
\title{Kyoto VR MQP Paper First Draft}
\author{William~Campbell, Cole~Granof, and Joseph~Petitti}
\date{\today}

@@

\maketitle

\begin{abstract}
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{abstract.jpg}
	% Note: you don't actually need the part in square brackets for the caption,
	% but if you omit it the regular caption text will be used for the List of
	% Figures entry.
	\caption[\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock]
	{\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock, National
		Gallery of Art, Washington, D.C.}
	\label{fig:abstract}
\end{figure}
\end{abstract}

@@

Finally, a thank you to our advisers: Professors Joshua Cuneo and Ralph Sutter.
Without their expert advice and feedback this project probably could not have
been completed.

@@

% now comes the table of contents, list of figures, and list of tables
% these should be single spaced
{
\linespread{1}

% add table of contents to itself
\tableofcontents
\addcontentsline{toc}{section}{Table of Contents}
\newpage

\listoffigures
\addcontentsline{toc}{section}{List of Figures}
\newpage

% we don't have any tables yet, but uncomment this when we do
%\addcontentsline{toc}{section}{List of Tables}
%\listoftables
%\newpage
}

@@

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. This means a few different things. For starters, many AR
apps and features available on smartphones offer very little in the way of
functionality or practicality; quite simply, they are primarily used for minor
spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one
of the most popular apps to use AR, Pokémon GO, primarily uses it's AR feature
to place a Pokémon in the world around you through your phone camera for you to
capture. But when it is in the world, it does not interact with anything around
it. It just floats a fixed distance away from you, simply placed on top of your
camera's video feed.

Additionally, in many cases where AR is used, the task could be accomplished as
well or better without AR~\autocite{theappsolutions2018}. Returning to the
Pokémon GO example, when the AR feature is left on while capturing a Pokémon,
the extra power needed for this feature drains the device faster, makes it
harder to hit the Pokémon with a Pokéball due to the model drifting in the
environment, and can even slow app performance, all of which detract from the
ability to play and enjoy the game.

@@

The company motive.io used to work on a product that would allow users to
create an engaging AR experience in the style of Pokémon Go. Their service
would have purportedly handled technical details such as hosting, storage, and
user accounts. The promotional video shows the creation of a location-based AR
game where the user pretends to hack into ATMs using the real-world locations
of ATMs in a city\autocite{odom2017}.

@@

\subsubsection{First Round of Field Testing}
\label{sec:firstRoundOfFieldTesting}

@@

@@

\printbibliography
\addcontentsline{toc}{section}{References}

>>>>

% useful packages
\usepackage[utf8]{inputenc} % UTF-8 support
\usepackage{minted} % for code snippets
\usepackage[american]{babel} % for changing particular titles
\usepackage{csquotes} % recommended for biblatex
\usepackage{graphicx} % for images
\usepackage[gen]{eurosym} % for literally just the euro symbol

\usepackage{lipsum} % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex} % citations
\usepackage[page, titletoc, title]{appendix} % labeled appendices
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref} % hyperlinks
\usepackage{setspace} % setting custom spacing

% more breathing room
\setminted{fontsize=\small,baselinestretch=1}

@@

% stuff for LaTeX to know
\bibliography{references}
\graphicspath{ {./images/} } % put images in here
\title{%
	\huge ARuko and Editour: \\
	\Large A Platform for Augmented Reality Tour Guide Apps}
\author{William~Campbell, Cole~Granof, and Joseph~Petitti}
\date{October 11, 2019}

@@

% draw the title page
\maketitle

% more breathing room
\setstretch{1.5}

\begin{abstract}
	% abstract goes here
	\begin{figure}[h]
		\centering
		\includegraphics[width=\textwidth]{abstract.jpg}
		% Note: you don't actually need the part in square brackets for the
		% caption, but if you omit it the regular caption text will be used for
		% the List of Figures entry.
		\caption[\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock]
		{\textit{Number 1, 1950 (Lavender Mist)}, Jackson Pollock, National
			Gallery of Art, Washington, D.C.}
		\label{fig:abstract}
	\end{figure}
\end{abstract}

@@

Finally, a thank you to our advisers, Professors Joshua Cuneo and Ralph Sutter.
Without their expert advice and feedback this project probably could not have
been completed.

@@

% now comes the table of contents, list of figures, and list of tables
% these should be single spaced
\begin{singlespace}
	\tableofcontents
	% add table of contents to itself
	\addcontentsline{toc}{section}{Table of Contents}
	\newpage

	\listoffigures
	\addcontentsline{toc}{section}{List of Figures}
	\newpage
\end{singlespace}

% we don't have any tables yet, but uncomment this when we do
%\addcontentsline{toc}{section}{List of Tables}
%\listoftables
%\newpage

@@

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. This means a few different things. For starters, many AR
apps and features available on smartphones offer very little in the way of
functionality or practicality; quite simply, they are primarily used for minor
spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one of
the most popular apps to use AR, \textit{Pokémon Go}, primarily uses it's AR
feature to place a Pokémon in the world around you through your phone camera for
you to capture. But when it is in the world, it does not interact with anything
around it. It just floats a fixed distance away from you, simply placed on top
of your camera's video feed.

Additionally, in many cases where AR is used, the task could be accomplished as
well or better without AR~\autocite{theappsolutions2018}. Returning to the
\textit{Pokémon Go} example, when the AR feature is left on while capturing a
Pokémon, the extra power needed for this feature drains the device faster, makes
it harder to hit the Pokémon with a Pokéball due to the model drifting in the
environment, and can even slow app performance, all of which detract from the
ability to play and enjoy the game.

@@

The company motive.io used to work on a product that would allow users to create
an engaging AR experience in the style of \textit{Pokémon Go}. Their service
would have purportedly handled technical details such as hosting, storage, and
user accounts. The promotional video shows the creation of a location-based AR
game where the user pretends to hack into ATMs using the real-world locations of
ATMs in a city\autocite{odom2017}.

@@

\subsubsection{Initial Field Testing}
\label{sec:initialFieldTesting}

@@

\subsubsection{Final Field Testing}
\label{sec:finalFieldTesting}

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of the ARuko in order to conduct some final testing.

@@

% references should be single spaced
\begin{singlespace}
	\printbibliography
	\addcontentsline{toc}{section}{References}
\end{singlespace}
